Naming Anonymous JavaScript Functions

### 2011-04-01 papers/splash-wavefront2011/sigplanconf-template.tex
edits section 3, but could not check with latex

\section{Introduction}
The unique and important role of JavaScript in web programming is undeniable. Along with the wave of ``Web 2.0", JavaScript has become the inevitable part of almost every modern web site. This language is used by all of the web's 100 most popular sites\footnote[1]{http://www.alexa.com}. It is very likely that JavaScript keeps this crucial role for the next few years or even the next decade. Along with the growth of demands for more comprehensive user interfaces, the size and the complexity of web applications is increasing. Morover, JavaScript is also becoming a general purpose computing platform with office applications \cite{JSOffice, JSOffice2}, browsers \cite{FAO, GCE} and development environments \cite{Ingalls} being developed in JavaScript \cite{Richards}. There are also proposals for employing JavaScript in server-side applications \cite{SSJSR, CJS}.

To cope with these large and sophisticated systems, JavaScript developers turn to better development tools. These tools analyze then represent the program in ways that the developer might only be able to imagine through substaintial time-consuming reading of source code.  One prime example is a runtime debugger: the developer can halt a running program and examine the program state and execution call stack. All of these tools need to express program artifacts in a compact way the developer can understand.  For example, the debugger needs to present the execution call stack so the developer can understand which functions are currently active.  Obviously a particularly good compact representation would be a name given by the developer in the source code. However, the JavaScript language itself does not require names for many program artifacts and -- as we shall see -- nameless or anonymous artifacts are more common than named ones. Anonymous artifacts prevent tools from communcating effectively with developers.

@@

In this paper, we analyze function creation and consumption in ten large, well-known projects. We show that within these projects less than 7\% of the function objects are named. We propose an automated approach based on extracted data from the source code for naming JavaScript functions. The candidate function names can be used in debuggers for more descriptive object summaries and callstack view, or in integration with proposed JavaScript typing systems for providing modern editing features in development environments.

@@

If you are unfamilar with JavaScript or other functional programming languages, you might imagine that developers would naturally select the form with names, simply as an organizational tool. However this is not the case. Functions in JavaScript are first-class objects. They can be assigned to any variable or object property, or passed as an argument to a function. Consequently JavaScript programmers can use this constructs to organize their thinking about the program, without the use of function names.

@@

\begin{figure*}[htp]
\centerline{
\subfigure[Google Chrome Debugger]{\label{fig_object_second_case}\includegraphics[width=0.47\textwidth,height=.15\textheight]{pic/chrome-objects.jpg}}
\hfil
\subfigure[Firebug]{\label{fig_object_first_case}\includegraphics[width=.47\textwidth,height=.15\textheight]{pic/fbug-objects.jpg}}}
\caption{The screenshot of veriables view of Google Chrome and Firebug JavaScript debuggers displaying the same program state.}
\label{debuggers-objects}
\end{figure*}

% JJB TODO
% It is common that the same function is called by various names in different contexts. 
%Therefore, it is usually very difficult to recall the function operation from its local name. 
%Developers have usually the option to look at the function code, but it becomes tedious
% and time-consuming when developer has to do it over and over again.

%Once a statement which defines a function is evaluated, a new {\small\texttt{Function}} 
%object is created. Notice that, depending on the times a function definition is evaluated, 
%zero to many {\small\texttt{Function}} objects can be created from the same definition. 
%To classify {\small\texttt{Function}} objects created by the same code, we call every 
%script defines a function as a \textit{function body}.

To understand the consequences of anonymous funcitons on development tools we will focus on one example, the impact on debuggers.
Two main issues apear in debuggers due to the lack of function name. First, object constructor name, which can faciliate understanding the object value, is not available in the object summary. Second, the callstack view is usually full of \textit{anonymous} functions and therefore much less informative. We disscuss these issues in the next two subsections.

@@

Figure~\ref{js-code} demonstrates an excerpt of a JavaScript code. We set a breakpoint on line 13 and examin the runtime elements at this breakpoint by two JavaScript debuggers, Google Chrome and Firebug (Figure~\ref{debuggers-objects}). Two objects assigned to variables {\small\texttt{foo}} and {\small\texttt{bar}} are constructed by two different constructors: {\small\texttt{FOO}} and {\small\texttt{BAR}}. However, Google Chrome debugger shows the general class of {\small\texttt{Object}} as the summary for both objects. The developer has to expand the object nodes to recognize their similarities and differences. Firebug classify objects in the same general class, but includes some of the object properties in the summary. These additional properties may hint developer about the object structures. {\small\texttt{FOO}} and {\small\texttt{BAR}} definitions at lines 19 and 22 explain the debuggers' behaviour; the function statements has no explicit name (identifier), therefore debuggers considered them as \textit{anonymous} functions.

@@

\subsection{Anonymous Function Names in Callstack View}
To illustrate the second issue, we pause the program (Figure~\ref{js-code}) at line 15 by a breakpoint. Figure~\ref{debuggers-callstack} shows how the program callstack is displayed in Google Chrome debugger and Firebug. The differences in the number of frames and line numbers between two callstacks are due to dissimilar event handling implementations in the underlying platforms. Google chrome shows \textit{anonymous} as the name of all functions excepting the first one. Firebug performs better by guessing three function names but it still fails in one case. In these cases, the information provided by debugger is useless and the developer has to locate the function source to understand or recall the function behaviour.

\begin{figure*}[htp]
\centerline{
\subfigure[Google Chrome Debugger]{\label{fig_second_case}\includegraphics[width=0.47\textwidth,height=.13\textheight]{pic/chrome-callstack.jpg}}
\hfil
\subfigure[Firebug]{\label{fig_first_case}\includegraphics[width=.47\textwidth,height=.13\textheight]{pic/fbug-callstack.jpg}}}
\caption{The screenshot of callstack view of Google Chrome and Firebug JavaScript debuggers paused at the same breakpoint.}
\label{debuggers-callstack}
\end{figure*}

Two other pieces of information which are important at function calls are {\small\texttt{this}} and argument values. In JavaScript, {\small\texttt{this}} like arguments is not defined by lexical scopes but it is bound once the function is called. The {\small\texttt{this}} value is missed in both views. The arguments values is shown in Firebug, but it still sufferes from similar issues explained for displaying object summaries.

\section{Discussion}
The anonymous functions problem is discussed in several articles and forums on the web \cite{DisplayName, Zaytsev}. Different solutions have been proposed and discussed by practitioners. A basic solution is a mechanism for naming functions by developers without affecting the variables in scopes. For example, a new property (e.g., \textit{displayName}) in the function object can be used for storing the function name, or the function name can be defined by an annotation. Although these solutions may help, they cause developers extra work.

We instead propose an almost automated approach for naming all functions by anlyzing the source code. Before getting into explaining the algorithm details we discuss the rationale behind some of decisions we made in this approach.

\subsection{What Makes a Good Function Name?}
A function name is basicly used to assist the developer to recall or understand the function behaviour. For a dveloper who is already familiar with the function, it works more like an identifier. However, this identifier should be easily recognized by the developer. For example, a naive proposal for the function name is a combination of the function file name and its first line number. Although it may work as an identifier, but it does not assist the develper to recall or understand the function behaviour.

 On the other hand, for a devloper who does not know the function, a function name should explains the function behaviour, or an abstraction of the function behaviour, or why/where the function is used/defined (e.g., to create the object \textit{foo}). A function name must not be too long that can not be displayed or read by the developer. For example, the function body explains the function behaviour well however it is not an appropriate function name.

\subsection{What Should be Named?} %// Function Object or Function Body}%What Should be Named?}
In JavaScript, functions can be accessed and changed like a regular object. Two function objects which are created from the same function body may have different properties. They also may have different enclosing scopes and therefore different behaviours. The question arises here is which one should be named, the function body or the function object? Although the actual enclosing scopes are not known until the function object creation, their structure can be almost known from the enclosing source code. Therfore the general function behaviour is mainly dependent to its function body and the enclosed function bodies.

\subsection{Context, Package and Function Names}
JavaScript does not support a standard packageing mechanism to be used for modular programming. Scripts are loaded from different files and executed within the same or different global objects. Developers usually use objects at the top level to encapsulate properties, objects and functions from a framework or library. The same mechanism is reused for defining subpackages. As the project size and the number of functions increases, the short function name will not be enough for recognizing the function. The developer also wants the class or the module contains the function. In addition to the package name, knowning the context (the enclosing function body) that contains the function can help in better understanding the function behaviour.

@@

\section{Automated Funcation Naming}
%	We instead, to tackle the aforementioned issues caused due to the lack of function names, propose automated function naming by anlyzing the source code. Before getting into details of how the function name is constructed, we discuss the rationale behind some of decisions we made in this approach.
  Developers usually understand and refer to function objects by aliases they use to access them. This fact particularly holds for permanent function objects such as classes and utility functions. However, functions with shorter lifetimes such as closures and callbacks are referred by their roles or purposes in the program. We employ these facts to construct an identifier for a function. We analyse the source code to locate alias(es) which the function object is assigned to. If the list of aliases is not empty we select the most appropriate one based on some ranking rules as the function name. Otherwise, we try to build a name based on the aliases that the function object somehow affect on their values. If there is no such alias then the function object is consumed as an argument in a chain of function calls that does not return any value or as a simple closure. In the case of function calls chain we use the most nested called function name for constructing the identifier. In the case of simple closure, we employ the function(s) identifier inside the closure to construct the identifier. 
  Many JavaScript projects have one or a few functions which are used for defining classes or registering function objects. These functions usually receive a string as the class name or function name. In our approach we need to get hint about these functions declarations. These hints can be usually described in simple regular expressions.

>>>>

\section{Introduction}
The unique and important role of JavaScript in web programming is undeniable. Along with the wave of ``Web 2.0", JavaScript has become the inevitable part of almost every modern web site. This language is used by all of the web's 100 most popular sites\footnote[1]{http://www.alexa.com}. It is very likely that JavaScript keeps this crucial role for the next few years or even the next decade. Along with the growth of demands for more comprehensive user interfaces, the size and the complexity of web applications is increasing. Moreover, JavaScript is also becoming a general purpose computing platform with office applications \cite{JSOffice, JSOffice2}, browsers \cite{FAO, GCE} and development environments \cite{Ingalls} being developed in JavaScript \cite{Richards}. There are also proposals for employing JavaScript in server-side applications \cite{SSJSR, CJS}.

To cope with these large and sophisticated systems, JavaScript developers turn to better development tools. These tools analyze then represent the program in ways that the developer might only be able to imagine through substantial time-consuming reading of source code.  One prime example is a runtime debugger: the developer can halt a running program and examine the program state and execution call stack. All of these tools need to express program artifacts in a compact way the developer can understand.  For example, the debugger needs to present the execution call stack so the developer can understand which functions are currently active.  Obviously a particularly good compact representation would be a name given by the developer in the source code. However, the JavaScript language itself does not require names for many program artifacts and -- as we shall see -- nameless or anonymous artifacts are more common than named ones. Anonymous artifacts prevent tools from communicating effectively with developers.

@@

In this paper, we analyze function creation and consumption in ten large, well-known projects. We show that within these projects less than 7\% of the function objects are named. We propose an automated approach based on extracted data from the source code for naming JavaScript functions. The candidate function names can be used in debuggers for more descriptive object summaries and call-stack view, or in integration with proposed JavaScript typing systems for providing modern editing features in development environments.

@@

If you are unfamiliar with JavaScript or other functional programming languages, you might imagine that developers would naturally select the form with names, simply as an organizational tool. However this is not the case. Functions in JavaScript are first-class objects. They can be assigned to any variable or object property, or passed as an argument to a function. Consequently JavaScript programmers can use this constructs to organize their thinking about the program, without the use of function names.

@@

\begin{figure*}[htp]
\centerline{
\subfigure[Google Chrome Debugger]{\label{fig_object_second_case}\includegraphics[width=0.47\textwidth,height=.15\textheight]{pic/chrome-objects.jpg}}
\hfil
\subfigure[Firebug]{\label{fig_object_first_case}\includegraphics[width=.47\textwidth,height=.15\textheight]{pic/fbug-objects.jpg}}}
\caption{The screenshot of variables view of Google Chrome and Firebug JavaScript debuggers paused on a breakpoint at line 15 of the program shown in Figure~\ref{js-code}.}
\label{debuggers-objects}
\end{figure*}

To understand the consequences of anonymous functions on development tools we will focus on one example, the impact on debuggers.
Two main issues appear in debuggers due to the lack of function name. First, object constructor name, which can facilitate understanding the object value, is not available in the object summary. Second, the call-stack view is usually full of \textit{anonymous} functions and therefore much less informative. We discuss these issues in the next two subsections.

@@

Figure~\ref{js-code} demonstrates an excerpt of a JavaScript code. We set a breakpoint on line 13 and examine the runtime elements at this breakpoint by two JavaScript debuggers, Google Chrome and Firebug (Figure~\ref{debuggers-objects}). Two objects assigned to variables {\small\texttt{foo}} and {\small\texttt{bar}} are constructed by two different constructors: {\small\texttt{FOO}} and {\small\texttt{BAR}}. However, Google Chrome debugger shows the general class of {\small\texttt{Object}} as the summary for both objects. The developer has to expand the object nodes to recognize their similarities and differences. Firebug classify objects in the same general class, but includes some of the object properties in the summary. These additional properties may hint developer about the object structures. {\small\texttt{FOO}} and {\small\texttt{BAR}} definitions at lines 19 and 22 explain the debuggers' behavior; the function statements has no explicit name (identifier), therefore debuggers considered them as \textit{anonymous} functions.

@@

\subsection{Anonymous Function Names in Callstack View}
To illustrate the second issue, we pause the program (Figure~\ref{js-code}) at line 15 by a breakpoint. Figure~\ref{debuggers-callstack} shows how the program call-stack is displayed in Google Chrome debugger and Firebug. The differences in the number of frames and line numbers between two call-stacks are due to dissimilar event handling implementations in the underlying platforms. Google chrome shows \textit{anonymous} as the name of all functions excepting the first one. Firebug performs better by guessing three function names but it still fails in one case. In these cases, the information provided by debugger is useless and the developer has to locate the function source to understand or recall the function behavior.

\begin{figure*}[htp]
\centerline{
\subfigure[Google Chrome Debugger]{\label{fig_second_case}\includegraphics[width=0.47\textwidth,height=.13\textheight]{pic/chrome-callstack.jpg}}
\hfil
\subfigure[Firebug]{\label{fig_first_case}\includegraphics[width=.47\textwidth,height=.13\textheight]{pic/fbug-callstack.jpg}}}
\caption{The screenshot of call-stack view of Google Chrome and Firebug JavaScript debuggers paused on a breakpoint at line 15 of the program shown in Figure~\ref{js-code}.}
\label{debuggers-callstack}
\end{figure*}

Two other pieces of information which are important at function calls are {\small\texttt{this}} and argument values. In JavaScript, {\small\texttt{this}} like arguments is not defined by lexical scopes but it is bound once the function is called. The {\small\texttt{this}} value is missed in both views. The \small\texttt{arguments} values is shown in Firebug, but it still suffers from the same issues as object summaries.

\section{Goals}
The anonymous functions problem is discussed in several articles and forums on the web \cite{DisplayName, Zaytsev}. Different solutions have been proposed and discussed by practitioners. A basic solution is a mechanism for naming functions by developers without affecting the variables in scopes. For example, a new property (e.g., \textit{displayName}) in the function object can be used for storing the function name, or the function name can be defined by an annotation. Although these solutions may help, they cause developers extra work, the annotation may be incorrectly recognized in programs that use the same property name for another purpose, and maintenance of the debugger becomes more difficult once the call-stack names can be overridden by user code.

We instead propose an almost automated approach for naming all functions by analyzing the source code. Before getting into explaining the algorithm details we discuss the rationale behind some of decisions we made in this approach.

\subsection{What Should Be Named?}

Once a statement which defines a function is evaluated, a new {\small\texttt{Function}} 
object is created.  The definition may be evaluated multiple times, and depending on the times a function definition is evaluated, 
zero to many {\small\texttt{Function}} objects can be created from the same definition. 
Two function objects which are created from the same function body may have different object properties added at runtime. They also may have different enclosing scopes and therefore different behaviors.  Thus our first 
decision: do we try to name the {\small\texttt{Function}} objects or the source that defines them?

For the common use cases, the different {\small\texttt{Function}} objects are bound to one or more properties of objects. The  names of these properties inform the developer about the role of the function in the actions of the object.  To determine the actions of the functions in turn, the developer must read the function source (or perhaps its documentation). Our function names serve to recall or summarize that source or documentation for the developer. Therefore we seek to name the source, the content between the curly braces known as the \textit{FunctionBody} in the standard\cite{ECMA}.

After reflection the reader may be puzzled by the preceding claim. On the one hand we claim that the function object instance may be bound to properties in multiple objects and those property names are not helpful for naming. On the other hand we will shortly introduce an algorithm that uses a property name (in part) to name a \textit{FunctionBody}. Ultimately we are relying on a subtle characteristic of JavaScript programming: the first binding of a \small\textit{Function}  to an object property differs from all other bindings because it is located in text near the \textit{FunctionBody} and thus developers associate this first binding with the meaning of the \small\textit{FunctionBody}.

\subsection{What Makes a Good Function Name?}
A function name is basically used to assist the developer to recall or understand the function behavior. For a developer who is already familiar with the function, it works more like an identifier. However, this identifier should be easily recognized by the developer. For example, a naive proposal for the function name is a combination of the function file name and its first line number. Although it may work as an identifier, but it does not assist the developer to recall or understand the function behavior.

 On the other hand, for a developer who does not know the function, a function name should explains the function behavior, or an abstraction of the function behavior, or why/where the function is used/defined (e.g., to create the object \textit{foo}). A function name must not be too long that can not be displayed or read by the developer. For example, the function body explains the function behavior well however it is not an appropriate function name.

\subsection{Context, Package and Function Names}
JavaScript does not support a standard packaging mechanism to be used for modular programming. Scripts are loaded from different files and executed within the same or different global objects. Developers usually use objects at the top level to encapsulate properties, objects and functions from a framework or library. The same mechanism is reused for defining subpackages. As the project size and the number of functions increases, the short function name will not be enough for recognizing the function. The developer also wants the class or the module contains the function. In addition to the package name, knowing the context (the enclosing function body) that contains the function can help in better understanding the function behavior.

@@

\section{Automated Function Naming}
%	We instead, to tackle the aforementioned issues caused due to the lack of function names, propose automated function naming by anlyzing the source code. Before getting into details of how the function name is constructed, we discuss the rationale behind some of decisions we made in this approach.
  Developers usually understand and refer to function objects by aliases they use to access them. This fact particularly holds for permanent function objects such as classes and utility functions. However, functions with shorter lifetimes such as closures and callbacks are referred by their roles or purposes in the program. We employ these facts to construct an identifier for a function. We analyse the source code to locate alias(es) which the function object is assigned to. If the list of aliases is not empty we select the most appropriate one based on some ranking rules as the function name. Otherwise, we try to build a name based on the aliases that the function object somehow affect on their values. If there is no such alias then the function object is consumed as an argument in a chain of function calls that does not return any value or as a simple closure. In the case of function calls chain we use the most nested called function name for constructing the identifier. In the case of simple closure, we employ the function(s) identifier inside the closure to construct the identifier. 
  Many JavaScript projects have one or a few functions which are used for defining classes or registering function objects. These functions usually receive a string as the class name or function name. In our approach we need to get hint about these functions declarations. These hints can be usually described in simple regular expressions.
